### 2017-01-06 doc/manuscript.Rmd
Created and added heatmap fig (with just TAGFA)
Included number of participants with 1, 2, 3 visits

cor_df <- analyze_corr()
```

@@

Recruitment for the Prospective Metabolism and Islet Cell Evaluation (PROMISE) 
cohort baseline visit took place between 2004-2006 from London and Toronto, 
Canada. Individuals were selected to participant if they met the eligibility 
criteria of having one or more risk factors for type 2 diabetes mellitus, 
including obesity, hypertension, family history of diabetes, and/or a history of
gestational diabetes or birth of a macrosomic infant. A total of 736 individuals
attended the baseline visit. Subsequent examinations occurred every three years,
with three examination visits completed to date (2004-2006, 2007-2009, and
2010-2013). Participants are contacted annually by telephone. The current study
sample used data on participants who did not have diabetes at baseline, who
returned for one or more of the follow-up examinations, and who had samples
available for fatty acid measurements (n=477; see the CONSORT diagram in 
`r cite_sf('consort')`. Metabolic characterization, anthropometric measurements,
and questionnaires on lifestyle and sociodemographics are collected at each
examination visit. Research ethics approval was obtained from Mount Sinai
Hospital and the University of Western Ontario, and all participants provided
written informed consent. Data collection methods were standardized across the 2
centres and research nurses were centrally trained.

@@

```{r fig_heatmap}
plot_heatmap(cor_df)
```

>>>>

cor_df <- analyze_corr()
cor_df_tagfa <- analyze_corr_tagfa()
```

@@

Recruitment for the Prospective Metabolism and Islet Cell Evaluation (PROMISE) 
cohort baseline visit took place between 2004-2006 from London and Toronto, 
Canada. Individuals were selected to participant if they met the eligibility 
criteria of having one or more risk factors for type 2 diabetes mellitus, 
including obesity, hypertension, family history of diabetes, and/or a history of
gestational diabetes or birth of a macrosomic infant. A total of 736 individuals
attended the baseline visit. Subsequent examinations occurred every three years,
with three examination visits completed to date (2004-2006, 2007-2009, and
2010-2013). Participants are contacted annually by telephone. The current study
sample used data on participants who did not have diabetes at baseline, who
returned for one or more of the follow-up examinations, and who had samples
available for fatty acid measurements (n=477; see the CONSORT diagram in 
`r cite_sf('consort')`; a total of `r calc_n_for_visits()[1]` attended all three
visits and had complete data). Metabolic characterization, anthropometric
measurements, and questionnaires on lifestyle and sociodemographics are
collected at each examination visit. Research ethics approval was obtained from
Mount Sinai Hospital and the University of Western Ontario, and all participants
provided written informed consent. Data collection methods were standardized
across the 2 centres and research nurses were centrally trained.

@@

```{r fig_heatmap}
plot_heatmap(cor_df)
```
```{r fig_heatmap_tagfa}
plot_heatmap(cor_df_tagfa, text = FALSE)
```
